Effects of CHILDREN's programs

### 2020-02-27 paper.Rnw
lg

\subsection{Previous research}

The previous research shows, that the childhood and youth is central in development of character traits and future opportunities. Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life. Heckmann and Carneiro (2003) show that especially early family factors determine the most of gaps in highschool attendance. Moreover, Deckers et. al. (2015) found by experiments in Germany, that children of higher educated parents are signficantly more patient. Children from parents with lower income and lower educational attainment typically have a lower weight at birth and are born in a later week of gestation, which are indicators for good initial conditions (Deckers et. al. 2015, Case et. al. 2002). Children that grow up in families with a low socio-economic status are often less mobile and more likely to keep to themselves. This could have a negative influence on their character development. For example, Chetty et. al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions. Furthermore, the result of Deckers et. al. (2020) provides causal evidence on the effect of social environment on prosocial attitudes. Being supported by a mentor could have a significant and persistant increase of elementary school children´s prosociality, in response to prosocial role models and intense social interactions. As investigated by Heckmann et. al. (2010) for a preschool education program in the US, investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.

>>>>

\subsection{Literature overview}

Previous research shows, that the childhood and youth is central in development of character traits and future opportunities. Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life. Heckmann and Carneiro (2003) show that especially early family factors determine the most of gaps in highschool attendance. Moreover, Deckers et. al. (2015) found by experiments in Germany, that children of higher educated parents are significantly more patient. Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions (Deckers et. al. 2015, Case et. al. 2002). Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves. This could have a negative influence on their character development. For example, Chetty et. al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions. Furthermore, the result of Deckers et. al. (2020) provides causal evidence on the effect of social environment on prosocial attitudes. Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions. Heckmann et. al. (2010) investigated a preschool education program in the US. He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
